A Real-Time Sonar Simulator for Automatic Target Recognition

### 2018-01-04 Simulator/article.tex
la2pdf commit - 2018:01:04	12:28:36	(to. 4.jan.)

\section{Transformation matrices}\label{transformation_matrices} 
We place, resize and orient objects in an euclidean 3D space using suitable transformation matrices that are applied to each of the object's vertices:
\begin{align}
\bmat{x_t \\ y_t \\ z_t \\ w}_\text{\parbox{1cm}{\setlength\baselineskip{0.3cm}transformed\\model}} &= \boldsymbol{T}\R\boldsymbol{S} \bmat{x \\ y \\ z \\ w}_\text{model}.
\end{align}
Here a model vertex at position $(x,y,z)$ is first scaled with $\boldsymbol{S}$, then rotated with $\R$
There is nothing special to these matrices, but we supply them here for completeness.

>>>>

\section{Transformation matrices}\label{transformation_matrices} 
%
We place, resize and orient objects in an euclidean 3D space using suitable transformation matrices that are applied to each of the object's vertices:
\begin{align}
\bmat{x_t \\ y_t \\ z_t \\ w}_\text{\parbox{1cm}{\setlength\baselineskip{0.3cm}transformed\\model}} &= \boldsymbol{T}\R\boldsymbol{S} \bmat{x \\ y \\ z \\ w}_\text{model}.
\end{align}
Here a model vertex at position $(x,y,z)$ is first scaled with $\boldsymbol{S}$, then rotated with $\R$
There is nothing special to these matrices, but we supply them here for completeness.
